Current State of Knowledge Representation Systems for Robotics

### 2011-11-24 krs-survey.tex
Filled sections on Formal logics and CWA/OWA

The idea of \emph{Cognitive Robotics} was coined in the early 1990s by Reiter.
In a chapter on that subject in \emph{Fondations of Artifical
Intelligence}~\cite{Levesque2007}, Levesque reminds about the manifesto they
wrote together in 1998:

@@

\paragraph{Logics formalism}

Which logic formalism (DL, 2nd order\ldots{})

On modal logics, see the remark of McCarthy, in \cite{McCarthy2007}, section 3

@@

\fixme{cf Levesque~\cite{Levesque2007}, section 24.3.2}

@@

@@

\subsubsection{Agent-dependent models}
\label{sect|multiple-models}

@@

Levesque~\cite{Levesque2007} distinguish two main tasks, the \emph{projection task} and the \emph{legality task}.

>>>>

The idea of \emph{Cognitive Robotics} was coined in the early 1990s by Reiter.
In a chapter on that subject in \emph{Fondations of Artifical
Intelligence}~\cite{Levesque2008}, Levesque reminds about the manifesto they
wrote together in 1998:

@@

\paragraph{Logic formalism}

The main role of a knowledge represenation system is to provide an adequate
representation system to store facts and concepts that can be informally
described in natural language.

Formal logic aims at providing such a representation system with the added
value of providing a tractable support for inference and reasoning.

Most (but not all) of the systems we survey rely on a particular logic
formalism. The choice of the formalism has a strong impact, on one side, on the
range of ideas that can be expressed conveniently (\emph{practical
expressiveness}) or at all (\emph{theoritical expressiveness}), on the other
side, on the ability to solve the inference problem (called
\emph{decidability}: is a given logical sentence true in my model?) in a
tractable manner.

A large number of logic formalism do exist, we shall summarize below the most
relevant for system actually deployed in current robotic architectures.

\emph{Predicate logic} is the family of logic formalisms the most commonly
found in knowledge representation. It distinguishes itself from the simpler
\emph{propositional logic} by the use of quantification to increase generality.
\emph{First-order logic} (FOL) is the subpart of \emph{predicate logic} where the
objects of \emph{predicates} (or \emph{formulae}) are simple \emph{terms},
while in \emph{higher-order logics}, predicates can be themselves objects of
other predicates.

The family of \emph{description logics}~\cite{Baader2008} also play an
important role. It is a subset of the first-order logic, with some extensions
in second-order logic. Description logics are notable because most of them are
known to be decidable. In description logic, axioms are build from
\emph{concepts}, \emph{roles} (that are unary or binary predicates) and
\emph{individuals}. \emph{Modal logics}, that allow for statement qualification
(like \emph{possibility} or \emph{necessity}) have been shown to be closely
related to description logics.

\fxfatal{On modal logics, see the remark of McCarthy, in \cite{McCarthy2007}, section 3}

One last class of logics that is of particular relevance for robotic
applications is the \emph{probabilistic logics} or \emph{bayesian logics}.
These logics provide a formal framework to reason on propositions whose truth
or falsity is uncertain.

\paragraph{Some examples}

\emph{The robot knows that a blue bottle is laying on the table.}

\emph{The robot knows that the human knows about the position of the bottle,
but the robot does not know what the human actually know about it.}

@@

The \emph{close world} (CWA) vs. \emph{open world} (OWA) assumption names a
modelling choice on the \emph{completeness} of a knowledge domain. In the close
world assumption, a proposition that can not be proven true is assumed to be
false (\emph{negation by failure}), while in the open world assumption, a
proposition may be considered either true, false or unknown.

This distinction is important in robotics were the robot may have to manipulate
concepts with only partial knowledge on them. For instance, let imagine a robot
that sees a bottle over a table, whose bottom is hidden by another object. The
robot can not prove that the bottle is indeed \emph{on} the table. A knowledge
representation system relying on the closed world assumption would then assume
the bottle is \emph{not} on the table ($\lnot R^{CWA}_{isOn}(bottle, table)$)
whereas with the open world assumption, the proposition $R^{OWA}_{isOn}(bottle,
table)$ would be undecided. Example in table~\ref{table|cwa-owa-example} provides
a simple, concerete example of consequences of the CWA/OWA choice on reasoning.

\begin{table}
	\begin{center}
	\begin{tabular}{ll}
	{\bf Action} & {\bf Part involved} \\
	\hline
	{\tt PickSoftly} & hand \\
	{\tt PickAndPlace} & arm, hand \\
	{\tt MoveArm} & arm \\
	\hline
	\end{tabular}
	\end{center}
	\caption{Assuming the question is: \emph{select actions that do not require
	to move the arm}, a CWA reasoner would return {\tt PickSoftly} whereas an
	OWA reasoner would not return anything if the {\tt PickSoftly} action is
	not explicitely said not to involve the arm.}
	\label{table|cwa-owa-example}
\end{table}

Domains constrained with the closed world assumption lead to more tractable
inference problems, and allow for instance the use of logic languages like
Prolog. Thus, several approaches exists to \emph{locally close} a domain (\cf
Levesque~\cite{Levesque2008}, section 24.3.2 for a summary of those).

@@

\paragraph{Knowledge alteration possibilities}

In DL -> always possible to modify the ABox, not always possible to alter the TBox

@@

\subsubsection{Possible-Worlds and Agent-dependent models}
\label{sect|possible-worlds}

\cite{Levesque2008}, p. 4

@@

Levesque~\cite{Levesque2008} distinguish two main tasks, the \emph{projection task} and the \emph{legality task}.
